\documentclass{book}
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{multirow}

\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {Figures/} }
\usepackage{float}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}

\usepackage{natbib,stfloats}

\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}
\usepackage{rotating}

\usepackage{tikz}
\usetikzlibrary{snakes}
\usetikzlibrary{patterns}

\usepackage{colortbl}
\newcolumntype{a}{>{\columncolor{yellow}}l}
\newcolumntype{b}{>{\columncolor{blue}}l}
\newcolumntype{d}{>{\columncolor{green}}l}

\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhead{}
\fancyhead[RO]{\textsl{\rightmark}} 
\fancyhead[LE]{\textsl{\leftmark}} 

\fancyfoot{} 
\fancyfoot[L]{T.B. Fraga. thoughts: COVID 19}
\fancyfoot[R]{\thepage}

\definecolor{cambridgeblue}{rgb}{0.64, 0.76, 0.68}
\definecolor{camel}{rgb}{0.76, 0.6, 0.42}
\definecolor{camouflagegreen}{rgb}{0.47, 0.53, 0.42}
\definecolor{desertsand}{rgb}{0.93, 0.79, 0.69}

\newenvironment{exerciseblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=camouflagegreen,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{exempleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=Brown!70,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{algorithmblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=Brown!40,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{dedication}
  {\clearpage           % we want a new page
   \thispagestyle{empty}% no header and footer
   \vspace*{\stretch{1}}% some space at the top 
   \itshape             % the text is in italics
   \raggedleft          % flush to the right margin
  }
  {\par % end the paragraph
   \vspace{\stretch{3}} % space at bottom is three times that at the top
   \clearpage           % finish off the page
  }

% para construção de diagramas

\tikzstyle{place}=[circle,draw=camouflagegreen!80,fill=desertsand!20,thick]
\tikzstyle{Ret}=[rectangle,draw=camouflagegreen!80,fill=desertsand!20,thick]
\tikzstyle{RoundRet}=[rectangle,draw=camouflagegreen!80,fill=desertsand!20,thick, rounded corners]

\begin{document}

About COVID 19. \\

Since the beginning of this pandemic, when the cases were still in China, I found it really strange that infected people were moving freely. \\

The only means of control was a thermometer shaped like a barcode reader. \\

As soon as I got news about the disease, I googled about old pandemics and the type of corona virus. I soon found out about its high contamination rate, which immediately scared me. \\

I believe I was the first person in Brazil to buy a box of gel alcohol bottles. \\

Some time passed and, unfortunately, in fact, the covid 19 infested Brazil as well as the rest of the world as we know it. \\

The corona virus contamination rate was already very well known. This has even been demonstrated in China. \\

Why the hell did the rulers simply not react by preventing the progression of contamination? \\

Then soon came the news about the absurd increase in share prices of companies in the pharmaceutical industry. \\

And then after a little over a year (as far as I remember) the vaccine came out, and lo and behold, they released the use of the vaccine, without meeting the necessary restrictions related to testing. \\

The world's population, faced with panic, did its part, taking the doses recommended by the governments. \\

I decided to wait and see. For me nothing made much sense. I wasn't panicking. The mortality rate was not reduced with the vaccine, the form of vaccination was inadequate, and the vaccines also did not prevent contamination. That was my perception. \\

Not to mention that the way it was progressing, it would be impossible to verify the effectiveness of the vaccines and the long-term damage, since there were never any test groups. \\

Every scientist knows that each and every experiment needs to be controlled, or it will not be possible to certify the results. Test groups are required. \\

And then after a few short years, we see the incredible advancement in technology. In particular linked to robotics and bioscience. \\

Only one question can destroy any and all rebuttals of my claims. \\

How many billions of minds would it take to train an artificial mind built through techniques like deep learning ? \\

I believe this answers everything. \\

And then I leave another question ? \\

Was it all worth it ? \\

So, finally, it is necessary to look for the culprits.\\ 


Well, I don't remember whose phrase this is, but it has been very present in my mind for the last few years. \\


\center " To find out who's to blame, just look at who's better profiting from it. "



\end{document}
