\documentclass{book}
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{multirow}

\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {Figures/} }
\usepackage{float}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}

\usepackage{natbib,stfloats}

\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}
\usepackage{rotating}

\usepackage{tikz}
\usetikzlibrary{snakes}
\usetikzlibrary{patterns}

\usepackage{colortbl}
\newcolumntype{a}{>{\columncolor{yellow}}l}
\newcolumntype{b}{>{\columncolor{blue}}l}
\newcolumntype{d}{>{\columncolor{green}}l}

\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhead{}
\fancyhead[RO]{\textsl{\rightmark}} 
\fancyhead[LE]{\textsl{\leftmark}} 

\fancyfoot{} 
\fancyfoot[L]{T.B. Fraga. thoughts: supreme consciousness.}
\fancyfoot[R]{\thepage}

\definecolor{cambridgeblue}{rgb}{0.64, 0.76, 0.68}
\definecolor{camel}{rgb}{0.76, 0.6, 0.42}
\definecolor{camouflagegreen}{rgb}{0.47, 0.53, 0.42}
\definecolor{desertsand}{rgb}{0.93, 0.79, 0.69}

\newenvironment{exerciseblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=camouflagegreen,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{exempleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=Brown!70,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{algorithmblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=camel!20,colframe=Brown!40,%
    colbacklower=camouflagegreen!75!camel!20,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{dedication}
  {\clearpage           % we want a new page
   \thispagestyle{empty}% no header and footer
   \vspace*{\stretch{1}}% some space at the top 
   \itshape             % the text is in italics
   \raggedleft          % flush to the right margin
  }
  {\par % end the paragraph
   \vspace{\stretch{3}} % space at bottom is three times that at the top
   \clearpage           % finish off the page
  }

% para construção de diagramas

\tikzstyle{place}=[circle,draw=camouflagegreen!80,fill=desertsand!20,thick]
\tikzstyle{Ret}=[rectangle,draw=camouflagegreen!80,fill=desertsand!20,thick]
\tikzstyle{RoundRet}=[rectangle,draw=camouflagegreen!80,fill=desertsand!20,thick, rounded corners]

\begin{document}

I belive that there is a supreme intelligence in our universe. Omnipresent, omniscient and omnipotent. \\

This intelligence has no form, it is neither good nor bad, because it falls short of these concepts. This being just is. It exists. \\

This has the capacity to guide man, and the entire universe of which man consists, as well as animals, vegetables and minerals, as well as the entire universe that cohabits these elements and the entire universe that is among these elements. \\

Before good and evil, there is order and chaos. \\

It guide so that there is order. \\

This supreme consciousness, cohabits, inspires and leads us to the path of wisdom. \\

When I say that I believe in God, or when I speak of God, it is this consciousness that I am referring to. \\

The strange thing is that if this consciousness seeks order. What causes chaos ? \\

It is possible that man is moving further and further away from this supreme consciousness. \\

Out of ignorance, man sees himself as a unique being, endowed with an existence of his own. And he fights for his self to prevail. \\

I believe that chaos is a digression force. And man, like everything else in the universe, is affected by this force. \\

Perhaps this explains man's ignorance. And the reason for such ignorance has prevailed. \\

Perhaps this is the struggle of existence. Not between good and evil but between order and chaos. \\

Nothing like a religion. I believe I can explain how to approach this supreme consciousness. \\

empty your mind and observe nature;

open your mind and listen to nature, as it often expresses itself;

have life projects but never be greedy;

seek and think often of music, art, philosophy, beauty, justice, etc.;

reflect, reflect, reflect;

know mathematics as a language;

learn to play a musical instrument;

appreciate good art;

appreciate philosophy;

seek your happiness but without exploiting or denigrating other beings;

strive hard to become the best at what you work for and believe in;

seek for yourself the cardinal virtues of Plato: wisdom, courage, moderation and justice;

never wish or do harm to other living beings;

exist and cohexist.

\end{document}
